Multi-Modal Modular Sensorimotor Contingencies for Deformable Objects

### 2016-08-26 twostagedo.tex
bib and piccies

There are several novel contributions. First, we show how the modular learning framework of \cite{harunowolpert,kopickiwyatt16} can be applied to deformable objects. Second, we show how each module can be decomposed into two separate learning problems, one for predicting forces from finger motions, and one for predicting object deformations from forces. Both models are generative, and we show how to learn each from data. Third, we show how to use these learned generative models not only to predict deformation, but also to classify an unidentified material.}

@@

As has been mentioned above there are several choices made in our modeling approach. The key choice is that the models are generative, which means that the models can be used to generate predicted sequences of behaviour. The specific approach taken here separates the predictive model out into components in two ways (see Figure~\ref{fig:system}). First we decompose models according to the modality of the information. In this case it is important to note that deformation has a particular causal structure related to the modes of sensing that are most easily employed. The forces and deformations can be measured separately, using force-torque and visual sensors respectively. The sensed forces are the cause of the observed deformation, and this can be exploited by sequencing the models by mode. Thus our approach can be seen as a sensorimotor contingency in which two contigencies are sequenced to produce an overall prediction. The input to the first predictor is the planned motion of the robot (or the joint torques), and this predictor predicts the resulting sequence of contact forces. The second predictor takes this sequence of forces as input and predicts a deformation sequence. Both models must be conditioned on the material and the object. This is where we decompose the model space in the second way, by specialising models to particular material and object combinations. This follows the principle of modular motor learning \cite{KopickiICRA11,haruno2001mosaic}, where prediction and control is specialised into many modules, each of which covers a relatively small portion of the input space, such as an object or material type. Thus we aim to acquire many specialist models of different deformable objects rather than a very few rather general models. The specific model forms we choose here could be replaced while retaining the overall scheme. In this paper we implement the scheme using a regression approach to force prediction, and we follow several other authors in employing a mass-spring system with learnable parameters for the deformation prediction.

>>>>

There are several novel contributions. First, we show how the modular learning framework of \cite{kopickiwyatt16, haruno2001mosaic} can be applied to deformable objects. Second, we show how each module can be decomposed into two separate learning problems, one for predicting forces from finger motions, and one for predicting object deformations from forces. Both models are generative, and we show how to learn each from data. Third, we show how to use these learned generative models not only to predict deformation, but also to classify an unidentified material.}

@@

As has been mentioned above there are several choices made in our modeling approach. The key choice is that the models are generative, which means that the models can be used to generate predicted sequences of behaviour. The specific approach taken here separates the predictive model out into components in two ways (see Figure~\ref{fig:system}). First we decompose models according to the modality of the information. In this case it is important to note that deformation has a particular causal structure related to the modes of sensing that are most easily employed. The forces and deformations can be measured separately, using force-torque and visual sensors respectively. The sensed forces are the cause of the observed deformation, and this can be exploited by sequencing the models by mode. Thus our approach can be seen as a sensorimotor contingency in which two contigencies are sequenced to produce an overall prediction. The input to the first predictor is the planned motion of the robot (or the joint torques), and this predictor predicts the resulting sequence of contact forces. The second predictor takes this sequence of forces as input and predicts a deformation sequence. Both models must be conditioned on the material and the object. This is where we decompose the model space in the second way, by specialising models to particular material and object combinations. This follows the principle of modular motor learning \cite{kopickiwyatt16,haruno2001mosaic}, where prediction and control is specialised into many modules, each of which covers a relatively small portion of the input space, such as an object or material type. Thus we aim to acquire many specialist models of different deformable objects rather than a very few rather general models. The specific model forms we choose here could be replaced while retaining the overall scheme. In this paper we implement the scheme using a regression approach to force prediction, and we follow several other authors in employing a mass-spring system with learnable parameters for the deformation prediction.
